\section{\textbf{Contributions}} 
\begin{itemize}
\textbf{How was the group managed?}
The group ran their own segments of the Assignment quite independantly, given our own commitments to other things such as Self-Learning, giving all members time to work on their sections at their own pace, and coming together towards the end to collate all of our work into a single git repository, and LaTeX file.
\end{itemize}

\begin{itemize}
\textbf{How did your team work together?}
Moments when our team worked together include in helping each other learn to use git/github, as well as helping format the central LaTeX document for all of our work to be placed.
\end{itemize}

\begin{itemize}
\textbf{What were some difficulties/challenges you had?}
Some difficulties we had included in choosing our respective electives in a way of being distinct from each other, especially in regards to electives from the Business School, in which Business Analytics/Business Information Systems can be closely linked to Information Systems and Data Science, other difficulties included communication between group members in regards to expectations, deadlines.
\end{itemize}

\begin{itemize}
\textbf{If you were to work with this same team again,what is one (or more?) change the team would make to work together more effectively? }
When choosing groups again, one should make a conscious effort to find people looking for a similar Level outcomes for their report, as discrepancies of expectations does not help the effectiveness of the group. I'd also set more rigid progress checkpoints and deadlines for the group, getting onto the work early before the crunch period of other assignments.
\end{itemize}

\begin{itemize}
\textbf{How was the work distributed between your team? }
Currently, the work was distributed between Jacob and Christian, Jacob was able to set up the Git repository with the required and well formatted LaTeX files within it. Building on from this, Christian and Jacob both worked on their two electives each, putting the work up on the common LaTeX file, along with their references for the bibliography. Among other sections, Christian wrote contributions while Jacob wrote and formatted Allocations, References, & introduction.
\end{itemize}

\begin{itemize}
\textbf{What did each team member do to contribute to the report?}
Christian and Jacob both contributed their reports on the suitable electives for their majors, Jacob formatted the report total, while Christian and Jacob both edited and amended the text within other sections.
\end{itemize}
